Asteroseismology of GD358 with complex C/O core profiles

### 2016-10-01 msnew.tex
a bit more modification (referee report)

We use {\sl Period04} \citep{Lenz05} for Fourier analysis and nonlinear least squares fitting to 
identify statistically significant peaks in each FT. We adopt the criterion that a peak must have 
an amplitude at least four times that of the average noise level in the given frequency range 
\citep{Provencal12}. This criterion places a 99.9\% probability that the peak represents a real signal,
and is not a result of random noise \citep{Scargle82, Provencal12}.  We define ``noise'' as the frequency-dependent 
average amplitude after prewhitening of the dominant frequencies. This is unquestionably a conservative estimate, 
as it is impractical to assume that all ``real'' frequencies are removed when determining
the noise level. This is certainly true for GD358, where amplitude modulation is present, and the peaks above $\approx$ 2500 $\mu$Hz\ 
are combination frequencies (see Section \ref{mode}, \citet{Provencal09}).  Fig.~\ref{noise} displays the average noise 
as a function of frequency for the 2007-2016 observing seasons. A similar plot for the 
archival data is presented in Fig. 3 of \citet{Provencal09}. We also calculated Monte Carlo 
simulations using the routine provided in {\sl Period04}.  This routine generates a set of light curves using 
the original times, the fitted frequencies and amplitudes, and added Gaussian noise. A least squares fit is 
performed on each simulated light curve, with the distribution of fit parameters giving the uncertainties. 
Our Monte Carlo results are consistent with our average noise estimates.

@@

Having established our baseline noise levels, we proceed to frequency selection and identification.
Our standard frequency selection procedure involves identifying the largest amplitude resolved peak in the FT,
fitting a sinusoid with that frequency to the data set, subtracting the fit from the light curve, 
recomputing the FT, examining the residuals, and repeating the process until no significant power 
remains. This technique is known as prewhitening. Prewhitening has inherent dangers, and must be 
employed with extreme vigilance, especially as we are aware of amplitude and/or frequency 
modulation in our data set. A detailed discussion of the prewhitening procedure and steps 
taken to minimize the effects of amplitude modulation is given in \citet{Provencal09}. Our final 
identifications of independent frequencies detected in each observing season are given in 
Table \ref{freq1} and Table \ref{freq2}.

>>>>

We use {\sl Period04} \citep{Lenz05} for Fourier analysis and nonlinear least squares fitting to 
identify statistically significant frequencies in each FT. We adopt the criterion that a peak must have 
an amplitude at least four times that of the average noise level in the given frequency range 
\citep{Provencal12}. This criterion places a 99.9\% probability that the peak represents a real signal,
and is not a result of random noise \citep{Scargle82, Provencal12}.  We define ``noise'' as the frequency-dependent 
average amplitude after prewhitening of the dominant frequencies. This is unquestionably a conservative estimate, 
as it is impractical to assume that the complete set of ``real'' frequencies are removed when determining
the noise level. This is inarguably true for GD358, where amplitude modulation is present, and the peaks above $\approx$ 2500 $\mu$Hz\ 
are combination frequencies (see Section \ref{mode}, \citet{Provencal09}).  Fig.~\ref{noise} displays the average noise 
as a function of frequency for the 2007-2016 observing seasons. A similar plot for the 
archival data is presented in Fig. 3 of \citet{Provencal09}. We also calculated Monte Carlo 
simulations using the routine provided in {\sl Period04}.  This routine generates a set of light curves using 
the original times, the fitted frequencies and amplitudes, and added Gaussian noise. A least squares fit is 
performed on each simulated light curve, with the distribution of fit parameters giving the uncertainties. 
Our Monte Carlo results are consistent with our average noise estimates.

@@

Having established our baseline noise levels, we proceed to frequency selection and identification.
Our standard frequency selection procedure identifies the largest amplitude resolved peak in the FT,
fits a sinusoid with that frequency to the data set, subtracts the fit from the light curve, 
recomputes the FT, examines the residuals, and repeates the process until no significant power 
remains. This technique is known as prewhitening. Prewhitening has inherent dangers, and must be 
employed with extreme vigilance, especially as we are aware of amplitude and/or frequency 
modulation in our data set. A detailed discussion of the prewhitening procedure and steps 
taken to minimize the effects of amplitude modulation is given in \citet{Provencal09}. Our final 
identifications of independent frequencies detected in each observing season are given in 
Table \ref{freq1} and Table \ref{freq2}.
